---
title: "activity"
author: "Ben Czekanski"
date: "March 6, 2016"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
library(ggplot2)
library(lubridate)
library(gridExtra)
library(knitr)
```

```{r}
activity <- read.csv("activity.csv")
activity2 <- activity[(is.na(activity$steps) == FALSE) ,]
activity2$date <- ymd(activity2$date)
activity2$date <- as.Date(activity2$date)
```

```{r}
total.steps = sum(activity2$steps)
hist(activity2$steps, xlab = "Steps", main = "Steps Histogram")
mean.steps = mean(activity2$steps)
median.steps = median(activity2$steps)
```

The total number of steps is `r total.steps`.
The mean number of steps is `r mean.steps`, and the median number of steps is `r median.steps`.

```{r}
activity2 %>%
  group_by(interval) %>%
  summarize(time.steps = mean(steps)) -> time.steps
time.steps %>%
  ggplot(aes(interval, time.steps)) +
    geom_line() +
    ylab("Steps")
```

```{r}
activity2 %>%
  group_by(interval) %>%
  summarize(avg_steps = mean(steps)) %>%
  arrange(desc(avg_steps)) %>%
  head(1) -> peak.int
 peak_int = peak.int$interval
 peak_steps = peak.int$avg_steps
```
The 5-minute interval that on average contains the most steps is interval `r peak_int`, and the number of steps on average is `r peak_steps`.
```{r}
activity %>%
  filter(is.na(steps) == TRUE) %>%
  summarize(steps_na = n()) %>%
  head(1) -> steps.na
```
The total number of rows with NAs is `r steps.na`.
```{r}
activity2 %>%
  group_by (date) %>%
  summarize(new.steps = mean(steps)) %>%
  head(100) -> new.steps
```
The missing data will be filled in by the average number of steps.

STILL NEEDS TO BE DONE

```{r}
activity$steps[which(is.na(activity$steps))] <- mean(activity$steps, na.rm =TRUE)
hist(activity$steps, xlab = "Steps", main = "Steps Histogram")
mean.steps1 = mean(activity$steps)
median.steps1 = median(activity$steps)
total.steps1 = sum(activity$steps)
```
The total number of steps is `r total.steps1`.
The mean number of steps is `r mean.steps1`, and the median number of steps is `r median.steps1`. The mean and median are the same as before but the totalnumber of steps is larger.


```{r}
activity %>%
  mutate(date = as.Date(date)) %>%
  mutate(day = weekdays(date)) %>%
  mutate(day == c("Saturday", "Sunday")) -> new

new %>%
  mutate(weekend = (day == c("Saturday", "Sunday"))) -> new
  
  w_end <- new[new$weekend == TRUE,]
  w_days <- new[new$weekend == FALSE,]

  w_end %>%
    ggplot(aes(interval, steps)) + geom_line() + ggtitle("Weekends")-> p1
  w_days %>%
    ggplot(aes(interval, steps)) + geom_line() + ggtitle("Weekdays")-> p2

grid.arrange(p1, p2, nrow=2)

  
 

```

